Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-06-01 EMNLP-demo-paper/system.tex
minor fix

\subsection{Input Sentences Perturbation}
\label{sec:perturb}
Due to the discrete nature of the natural language, automatically applying perturbation to a sentence for sensitivity analysis can be particularly challenging (compared to other domains, i.e., image), as small changes in words can lead to drastic differences in the semantics of the sentences.
To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}. However, synonym replacement does not guarantee the meaning of the sentence remains the same, and  \the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
%However, this method requires minimal computation and is easy to implement.

@@

\subsection{Prediction Visualization}
Efficient visual encoding for prediction is crucial for communicating the model behavior, and to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
%
For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.
A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.

>>>>

\subsection{Input Sentences Perturbation}
\label{sec:perturb}
Due to the discrete nature of the natural language, automatically applying perturbation to a sentence for sensitivity analysis can be particularly challenging (compared to other domains, i.e., image), as small changes in words can lead to drastic differences in the semantics of the sentences.
To reduce the potential semantic deviation, we first devise a straightforward perturbation method by replacing \emph{nouns} and \emph{verbs} by their synonyms in the WordNet~\cite{Miller1995}. However, synonym replacement does not guarantee the meaning of the sentence remains the same, and the WordNet often produces rare words or obscure usages that may lead to less meaningful sentences.
%However, this method requires minimal computation and is easy to implement.

@@

\subsection{Prediction Visualization}
Efficient visual encoding for prediction is crucial for communicating the model behavior, and to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
%
For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangular barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.
A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.
